The Concurrent Calculi Formalisation Benchmark

### 2024-09-29 coordination24/short-paper.tex
reorganization

\begin{credits}
\subsubsection{\ackname}
The work is partially supported by EPSRC EP/T006544/2, Independent
Research Fund Denmark RP-1 grant ``Hyben'', and Independent Research
Fund Denmark RP-1 grant ``MECHANIST''.

>>>>

\begin{credits}
\subsubsection{\ackname}
The work is partially supported by the UK Engineering and Physical Sciences Research Council (EPSRC) grants EP/T006544/2, EP/V000462/1 and EP/X015955/1; Independent
Research Fund Denmark RP-1 grant ``Hyben''; and Independent Research
Fund Denmark RP-1 grant ``MECHANIST''.
